---
title: "capstone"
output: html_document
---

Source : https://osf.io/ru5kc/?show=revision 

```{r}
library(broom)
library(mosaic)
library(dplyr)
library(tidyverse)
library(tidymodels)
library(discrim)
library(EBImage)
library(lavaan)
library(semPlot)
library(OpenMx)
library(tidyverse)
library(knitr)
library(kableExtra)
library(GGally)
library(crunch)
```

# SPIN Questionnaire 
```{r}
img = readImage("https://d33v4339jhl8k0.cloudfront.net/docs/assets/5bedba8804286304a71c50f5/images/5c4b7cb02c7d3a66e32daa4c/img-19274-1548450913-2068804204.png")
display(img, method = "raster")
```

# GAD Questionnaire
```{r}
img = readImage("https://therapymeetsnumbers.com/wp-content/uploads/2018/09/29-gad-7-1.jpg")
display(img, method = "raster")
```

# SLW Questionnaire

```{r}
img = readImage("https://d33v4339jhl8k0.cloudfront.net/docs/assets/5bedba8804286304a71c50f5/images/5c4b7cb2042863543ccc4054/img-19274-1548450910-1395548438.png")
display(img, method = "raster")
```



## The Data

```{r}
gd <-read.csv('GamingStudy_data.csv', header = TRUE, sep = ",")

gd <- as_tibble(gd)

gd

gd$GADE = as.factor(gd$GADE)
gd$Game = as.factor(gd$Game)
gd$Platform = as.factor(gd$Platform)
gd$earnings = as.factor(gd$earnings)
gd$whyplay = as.factor(gd$whyplay)
gd$Gender = as.factor(gd$Gender)
gd$Work = as.factor(gd$Work)
gd$Degree = as.factor(gd$Degree)
gd$Playstyle = as.factor(gd$Playstyle)
gd$Residence = as.factor(gd$Residence)

str(gd)
```

# Splitting the data in case I want to use it

```{r}
gd_split <- initial_split(gd, strata = GAD_T, prop = .75, .25)
gd_split

gd_train <- training(gd_split)
gd_test <- testing(gd_split)
```

# Looking for the outlier

```{r}
gd_lm <- lm(Hours~ GAD_T  + GAD1 + GAD2 + GAD3 + GAD4 + GAD5 + GAD6 + GAD7 + SWL1+SWL2+SWL3+SWL4+SWL5+SPIN1+SPIN2+SPIN3+SPIN4+SPIN5+SPIN6+SPIN7+SPIN8+SPIN10+SPIN11+SPIN12+SPIN13+SPIN14+SPIN15+SPIN16+SPIN17+Narcissism+Age+SWL_T+SPIN_T, data = gd)
gd_lm_tidy <- tidy(gd_lm, conf.int = TRUE)
gd_lm_tidy
```

```{r}
gd_lm_aug <- augment(gd_lm)
gd_lm_aug
```

```{r}
ggplot(gd_lm_aug, aes(y = .std.resid, x = .fitted )) + 
  geom_point() +
  geom_hline(yintercept = 0)  + 
  labs(title = "Standard Residuals Hours Before Getting Rid of Outliers", xlab = "Fitted", ylab = "Standard Residual")  
```

```{r}
ggplot(gd_lm_aug, aes(y = .resid, x = .fitted )) + 
  geom_point() +
  geom_hline(yintercept = 0)
```

```{r}
arrange(gd_lm_aug, desc(.std.resid))
```
```{r}
gd_lm_aug2 <- filter(gd_lm_aug, Hours < 113)
```

```{r}
gd_lm_aug2
```


```{r}
ggplot(gd_lm_aug2, aes(y = .resid, x = .fitted )) + 
  geom_point() +
  geom_hline(yintercept = 0)
```

```{r}
ggplot(gd_lm_aug2, aes(y = .std.resid, x = .fitted )) + 
  geom_point() +
  geom_hline(yintercept = 0) +
  labs(title = "Data After Getting Rid of the Outliers")
```

## I filter out the hours and NAs

```{r}
gd2 <- filter(gd, Hours < 113)
```

```{r}
gd2 <- gd2[complete.cases(gd2[ , c("Hours", "Narcissism", "Gender", "Age", "Game", "GAD_T", "SPIN_T", "SWL_T")]),]
```

## Showing the data now

```{r}
arrange(gd2, desc(Hours))
view(gd2)
```

## More graphs of the data

```{r}
ggplot(gd2, aes(x = GAD_T, y = log(Hours))) + geom_point()
```

```{r}
ggplot(gd2, aes(x = SWL_T, y = log(Hours))) + geom_point()
```

```{r}
ggplot(gd2, aes(x = SPIN_T, y = log(Hours))) + geom_point()
```


```{r}
ggplot(gd2, aes(x = SWL_T)) +
  geom_histogram(binwidth = 1, boundary = 3) + 
  labs(title = "SWL Total", xlab = "SWL Total Score", ylab = "Count") + 
  geom_vline(aes(xintercept = 5), colour="blue") + 
  geom_vline(aes(xintercept = 9), colour="blue") + 
  geom_vline(aes(xintercept = 31), colour="red") + 
  geom_vline(aes(xintercept = 35), colour="red") +
  ggtitle("Satisfaction With Life Total") + xlab("Total Score") + ylab("Count")
#Between the two separate line things are extrememly dissatisfied with life and extremely satisfied with life
```


```{r}
ggplot(gd2, aes(x = SPIN_T)) +
  geom_histogram(binwidth = 1, boundary = 3) +
  labs(title = "SPIN Total", xlab = "SPIN Total Score", ylab = "Count") +
  geom_vline(aes(xintercept = 21), colour="black") +
  geom_vline(aes(xintercept = 30), colour="blue") + 
  geom_vline(aes(xintercept = 40), colour="red") + 
  geom_vline(aes(xintercept = 50), colour="green") +
  ggtitle("Social Phobia Inventory Total") + xlab("Total Score") + ylab("Count")
#Lines indicate mild, moderate, severe, very severe social phobia
```

```{r}
ggplot(gd2, aes(x = GAD_T)) +
  geom_histogram(binwidth = 1, boundary = 3) +
  labs(title = "GAD Total", xlab = "GAD Total Score", ylab = "Count") + 
  geom_vline(aes(xintercept = 5), colour="black") +
  geom_vline(aes(xintercept = 10), colour="blue") +
  geom_vline(aes(xintercept = 15), colour="red") +
  ggtitle("General Anxiety Disorder Total") + xlab("Total Score") + ylab("Count")
#Lines represent mild, moderate, and severe levels
```


```{r}
ggplot(gd2, aes(x = Hours)) +
  geom_histogram(binwidth = 5, boundary = 3)
```

```{r}
ggplot(gd2, aes(x = log(GAD4))) +
  geom_histogram(binwidth = .5, boundary = 3)
```
## Distribution between the different games


```{r}
library(ggplot2)
ggplot(data=gd2, aes(x=GAD_T,fill = Game)) + geom_histogram()
```

```{r}
library(ggplot2)
ggplot(data=gd2, aes(x=SPIN_T,fill = Game)) + geom_histogram()
```


```{r}
library(ggplot2)
ggplot(data=gd2, aes(x=SWL_T,fill = Game)) + geom_histogram()
```

# ANOVA

## GADT

```{r}
ggplot(gd2, aes(y = GAD_T, x = Game)) +
    geom_boxplot() + coord_flip()
```

```{r}
lmgadaov <- lm(GAD_T ~ Game, data = gd2)
summary(lmgadaov)
```


```{r}
gd2an <- aov(GAD_T ~ Game, data = gd2)
gd2ant <- tidy(gd2an)
gd2ant

pdist("f", df1 = gd2ant$df[1], df2 = gd2ant$df[2], df3 = gd2ant$df[3], df4 = gd2ant$df[4], df5 = gd2ant$df[5], df6 = gd2ant$df[6], df7 = gd2ant$df[7], df8 = gd2ant$df[8], df9 = gd2ant$df[9], df10 = gd2ant$df[10],
      q = gd2ant$statistic[1],
      invisible = TRUE)
```


```{r}
P1 <-gd2ant$p.value[1]
P1
```

So then there is no evidence to relate GAD scores by difference in game. 


## SPINT


```{r}
ggplot(gd2, aes(y = SPIN_T, x = Game)) +
    geom_boxplot() + coord_flip()
```

```{r}
lmspaov <- lm(SPIN_T ~ Game, data = gd2)
summary(lmspaov)
```

```{r}
gd2an2 <- aov(SPIN_T ~ Game, data = gd2)
gd2ant2 <- tidy(gd2an2)
gd2ant2

pdist("f", df1 = gd2ant2$df[1], df2 = gd2ant2$df[2], df3 = gd2ant2$df[3], df4 = gd2ant2$df[4], df5 = gd2ant2$df[5], df6 = gd2ant2$df[6], df7 = gd2ant2$df[7], df8 = gd2ant2$df[8], df9 = gd2ant2$df[9], df10 = gd2ant2$df[10],
      q = gd2ant2$statistic[1],
      invisible = TRUE)
```


```{r}
P2 <-gd2ant2$p.value[1]
P2
```

So then there is evidence of a difference in spin scores between games. 


## SWLT

```{r}
ggplot(gd2, aes(y = SWL_T, x = Game)) +
    geom_boxplot() + coord_flip() +
    ggtitle("Game Vs. SWL Total") + ylab("SWL Total Score") + xlab("Game Played")
```

```{r}
lmswaov <- lm(SWL_T ~ Game, data = gd2)
summary(lmswaov)
```



```{r}
gd2an3 <- aov(SWL_T ~ Game, data = gd2)
gd2ant3 <- tidy(gd2an3)
gd2ant3

pdist("f", df1 = gd2ant3$df[1], df2 = gd2ant3$df[2], df3 = gd2ant3$df[3], df4 = gd2ant3$df[4], df5 = gd2ant3$df[5], df6 = gd2ant3$df[6], df7 = gd2ant3$df[7], df8 = gd2ant3$df[8], df9 = gd2ant3$df[9], df10 = gd2ant3$df[10],
      q = gd2ant3$statistic[1],
      invisible = TRUE)
```


```{r}
P3 <-gd2ant3$p.value[1]
P3
```

So there is a difference between games in swl scores 

## Narcissism & Hours

```{r}
lmncaov <- lm(Narcissism ~ Game, data = gd2)
summary(lmncaov)
```

Some significance between these values, but really not much of a difference between groups when pertaining to narcissism

```{r}
lmhraov <- lm(Hours ~ Game, data = gd2)
summary(lmhraov)
```

There is a deeply significant difference between groups when pertaining to hours played. 

## But as all data sets have their limitations 

```{r}
tally(~ Game, data = gd2)
```

```{r}
par(las=2)
counts <- table(gd$Game)
barplot(counts, main="Game", horiz=TRUE, cex.names=0.8
  )
```


## So we take every game but LoL out

```{r}
gdlol <- filter(gd2, Game == "League of Legends")
```

```{r}
gdlol <- gdlol[complete.cases(gdlol[ , c("Hours", "Narcissism", "Game", "GAD_T", "SPIN_T", "SWL_T")]),]
```



```{r}
str(gdlol)
gdlol
```

```{r}
specmod <- "
# Path c (direct effect)
GAD_T ~ c*Hours

# Path a
Narcissism ~ a*Hours

# Path b 
GAD_T ~ b*Narcissism

# Indirect Effect (a*b)
ab := a*b
"

fitmod <- sem(specmod, data = gdlol)

summary(fitmod, fit.measures = TRUE, rsquare = TRUE)
```

```{r}
specmod2 <- "
# Path c (direct effect)
SPIN_T ~ c*Hours

# Path a
Narcissism ~ a*Hours

# Path b 
SPIN_T ~ b*Narcissism

# Indirect Effect (a*b)
ab := a*b
"

fitmod2 <- sem(specmod2, data = gdlol)

summary(fitmod2, fit.measures = TRUE, rsquare = TRUE)
```

```{r}
specmod3 <- "
# Path c (direct effect)
SWL_T ~ c*Hours

# Path a
Narcissism ~ a*Hours

# Path b 
SWL_T ~ b*Narcissism

# Indirect Effect (a*b)
ab := a*b
"

fitmod3 <- sem(specmod3, data = gdlol)

summary(fitmod3, fit.measures = TRUE, rsquare = TRUE)
```


```{r}

fitmod33 <- sem(specmod3, data = gdlol, se = "bootstrap", bootstrap = 100)
parameterEstimates(fitmod33, ci=TRUE, level = .95, boot.ci.type="perc")
```

```{r}

fitmod22 <- sem(specmod2, data = gdlol, se = "bootstrap", bootstrap = 100)
parameterEstimates(fitmod22, ci=TRUE, level = .95, boot.ci.type="perc")
```

```{r}
fitmod11 <- sem(specmod, data = gdlol, se = "bootstrap", bootstrap = 100)
parameterEstimates(fitmod11, ci=TRUE, level = .95, boot.ci.type="perc")
```

```{r}
model <-'
SWL_T ~ Hours + Age + Narcissism 
SPIN_T ~ Hours + Age + Narcissism 
GAD_T ~ Hours + Age + Narcissism 


Hours~~Age 
Hours~~ Narcissism 
Age~~Narcissism

SWL_T~ GAD_T + SPIN_T
'
```


```{r}
fit <- lavaan(model, data = gdlol, auto.var = TRUE)
summary(fit, fit.measures = TRUE, standardized=TRUE, rsquare = TRUE)
```

```{r}
parameterEstimates(fit)
```


```{r}
semPaths(fit, what = "std", whatLabels = "std", style="lisrel", edge.label.cex=1, curvePivot=TRUE)
```


```{r}
semPaths(fit, what= "paths", whatLabels="par", style="lisrel", layout="circle2", rotation = 1)
```

# What if we took out the people who do and do not play for fun??

```{r}
gd4fun <- filter(gdlol, whyplay == "having fun")

gd4fun <- gd4fun[complete.cases(gd4fun[ , c("Hours", "Narcissism", "Gender", "Age", "Game", "GAD_T", "SPIN_T", "SWL_T")]),]

#So I filter out the people who responded to why do I play as having fun. 
```


```{r}
fit <- lavaan(model, data = gd4fun, auto.var = TRUE)
summary(fit, fit.measures = TRUE, standardized=TRUE, rsquare = TRUE)
```


```{r}
parameterEstimates(fit)
```

```{r}
semPaths(fit, what = "std", whatLabels = "std", style="lisrel", edge.label.cex=1, curvePivot=TRUE)
```

```{r}
semPaths(fit, what= "paths", whatLabels="par", style="lisrel", layout="circle2", rotation = 1)
```

## Now we take out the people who only play to have fun

```{r}
gdnfun <- filter(gdlol, whyplay != "having fun")

gdnfun <- gdnfun[complete.cases(gdnfun[ , c("Hours", "Narcissism", "Gender", "Age", "Game", "GAD_T", "SPIN_T", "SWL_T")]),]

#So I take out the people who responded to why do I play as having fun. Mainly to see if there is any kind of different response relating to narcissism.
```


```{r}
fit <- lavaan(model, data = gdnfun, auto.var = TRUE)
summary(fit, fit.measures = TRUE, standardized=TRUE, rsquare = TRUE)
```

```{r}
parameterEstimates(fit)
```
```{r}
semPaths(fit, what = "std", whatLabels = "std", style="lisrel", edge.label.cex=1, curvePivot=TRUE)
```

```{r}
semPaths(fit, what= "paths", whatLabels="par", style="lisrel", layout="circle2", rotation = 1)
```